---
title: "Geospatial Timeseries Animation"
date: '2023-06-16'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
**Data Source:** [The Database of Religious History](https://religiondatabase.org/)



**Languages:** *Python*



**Libraries:** 


* Webscraping:  *selenium*
* Data Cleaning: *pandas, geopandas, google geocoding api, countryconverter*
* Visualization: *pandas, numpy and plotly*


**Code and Notebooks:** [Github link](https://github.com/AmberHabib/religious_history_project)


I created this animation to understand the formation and spread of new religious groups over time across the globe. I took a lot of care in making this plot, from scraping the data from [the source](https://religiondatabase.org/browse/regions) to creating an interactive visualization with the aim of accomodating as much information as possible in a single animation. I tried my best to reference and map  the regions with ancient names  accurately. Please contact me via email if you find errors.

[Click here](religious_history_EDA.html) to see more EDA plots for this data. 

```{r, echo = FALSE, out.width="100%"}
knitr::include_url("religious_history_project/religion_anim_slider_scattermaps_final.html", height="600")
```